---
output: github_document
---

# DiabetesPredictor

## Overview

**"DiabetesPredictor"** is a reproducible machine learning software package developed for the **BIO215 Capstone Project**. It encapsulates a pre-trained Random Forest classifier derived from **Kaggle: the BRFSS 2015 dataset** to predict diabetes risk based on clinical health indicators.

## Features

-   **Pre-trained Model**: Includes a high-performance Random Forest model (AUC \~).
-   **Automated Preprocessing**: Automatically handles factor level mapping (e.g., converting numeric inputs like `1` to `Excellent` for General Health) to ensure robust inference.

## Installation

You can install the development version of DiabetesPredictor from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("conlinzyang/DiabetesPredictor")
```

## Usage Example

This package comes with built-in example data to demonstrate the prediction workflow.

```{r, eval = FALSE}
library(DiabetesPredictor)

# 1. Load the built-in sample data (first 10 rows of the dataset)
# Using system.file to locate the data within the installed package
data_path <- system.file("extdata", "sample.csv", package = "DiabetesPredictor")
input_data <- read.csv(data_path)

# Display raw input
head(input_data, 3)

# 2. Run Prediction
# The function automatically sanitizes the input and loads the internal model
predictions <- predict_diabetes(input_data)

# 3. View Results
print(predictions)
```

## Model Information

-   **Algorithm**: Random Forest
-   **Training Data**: CDC Behavioral Risk Factor Surveillance System (BRFSS) 2015 <https://www.kaggle.com/datasets/prosperchuks/health-dataset/data?select=diabetes_data.csv>.
-   **Input Features**: HighChol, HighBP, DiffWalk, Age, GenHlth, BMI, HvyAlcoholConsump, CholCheck.

## **Acknowledgements**

-   **Xiaoyu Zhang**: Model Trainer
-   **Zhicheng Yang**: Package Encapsulator
